코로나19

### 2020-02-29 cd-corona.Rmd
added korean corona cases

---
title: "코로나19"
subtitle: "대쉬보드"
output: 
  flexdashboard::flex_dashboard:
    theme: readable
    orientation: rows
    vertical_layout: scroll
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```

@@

@@

>>>>

---
title: "코로나19"
subtitle: "대쉬보드"
output: 
  flexdashboard::flex_dashboard:
    theme: readable
    orientation: rows
    vertical_layout: fill
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(extrafont)
loadfonts()

@@

### 검사자수

```{r tested}
valueBox(NA, 
         icon = "fa-vial",
         color = "primary")
```

@@

```{r ingest-corona-google, warning=FALSE, eval=FALSE}
## 데이터셋 --------------------
library(googlesheets4)
library(tidyverse)
library(lubridate)

cv_kor <- read_sheet('https://docs.google.com/spreadsheets/d/1fODH5PZJw9jxwV2GRe85BRQgc3mxdyyIpQ0I6MDJKXc/edit#gid=0')

cv_kor_df <- cv_kor %>% 
  select(날짜, 확진자=`누적 확진자수`, 검사자 = `누적 검사자수`, 사망자, 회복자=`누적 격리해제`) %>% 
  arrange(날짜) %>% 
  mutate(일자 = as.Date(날짜)) %>% 
  group_by(일자) %>% 
  summarise(검사자 = last(검사자),
               확진자 = last(확진자),
               사망자 = last(사망자),
               회복자 = last(회복자)
            )  %>% 
  padr::pad(.)

cv_kor_df %>% 
  write_rds("data/cv_kor_df.rds")
```

### 검사자수

```{r kor-tested}
cv_kor_df  <-  
  read_rds("data/cv_kor_df.rds")

kor_tested <- cv_kor_df %>% 
  select(검사자) %>% 
  slice(n()) %>% pull

valueBox(scales::comma(kor_tested), 
         icon = "fa-vial",
         color = "primary")
```

```{r kor-infected}
kor_infected <- cv_kor_df %>% 
  select(확진자) %>% 
  slice(n()) %>% pull

valueBox(scales::comma(kor_infected), 
         icon = "fa-procedures",
         color = "warning")
```

```{r kor-death}
kor_death <- cv_kor_df %>% 
  select(사망자) %>% 
  slice(n()) %>% pull
valueBox(scales::comma(kor_death), 
         icon = "fa-skull",
         color = "danger")
```

```{r kor-recovered}
kor_recovered <- cv_kor_df %>% 
  select(회복자) %>% 
  slice(n()) %>% pull

valueBox(scales::comma(kor_recovered), 
         icon = "fa-walking",
         color = "success")
```

```{r kor-df}
cv_kor_df %>%
  arrange(desc(일자)) %>% 
  DT::datatable(filter = 'top',  
          options = list(   searchHighlight = TRUE, pageLength = 15,
                            dom = 'Bfrtip',
                            buttons = c('copy', 'csv', 'excel', 'pdf', 'print')),
          extensions = 'Buttons') %>% 
  DT::formatRound(c("검사자", "확진자", "사망자", "회복자"), digits=0)
```

```{r kor-df-viz}

korea_theme <- theme_classic(base_family = "NanumGothic") +
  theme(legend.position = "none") +
  theme(legend.background = element_rect(fill = "gainsboro")) +
  theme(plot.background = element_rect(fill = "gainsboro")) +
  theme(panel.background = element_rect(fill = "gainsboro"))

cv_kor_plot <- cv_kor_df %>% 
  gather(유형, 사람수, -일자) %>% 
  mutate(유형 = factor(유형, levels=c("검사자", "확진자", "회복자", "사망자"))) %>% 
  ggplot(aes(x=일자, y=사람수, color=유형)) +
    geom_line() +  
    geom_point() +
    facet_wrap(~유형, scale="fixed") +
    scale_y_continuous(labels = scales::comma_format(scale = 1)) +
    korea_theme +
    labs(x="", y="") +
    scale_color_viridis_d(option = "magma",
                     direction = -1)

plotly::ggplotly(cv_kor_plot)
```
